% LaTeX resume using res.cls
\documentclass[line,margin]{res}
\topmargin=-0.3in
\usepackage{enumitem}
\usepackage{hyperref} 
\setlist[itemize]{leftmargin=*}

\begin{document}


\name{Marcos A. Tanaka}


\address{\sl \href{https://marcosatanaka.com}{marcosatanaka.com} --- \href{mailto:marcosatanaka@gmail.com}{marcosatanaka@gmail.com}}


\begin{resume}


\section{PROFESSIONAL \\ EXPERIENCE}
  {\bf DB1 Global Software} \hfill {\bf Jul 2018---Present} \\
  iOS Developer \hfill {\sl Maring\'a, PR}\\[-6pt]
  \begin{itemize}
    \item {\sl Mentored new developers.}
    \item {\sl Developed the \href{https://apps.apple.com/us/app/id1490242421}{Omni Card iOS app}.}
    \item {\sl Developed a registration flow that enables customers to open a digital checking account in the \href{https://apps.apple.com/br/app/omni-banco/id1369601365}{Omni bank iOS app}. This helped increase the average number of account proposals per week by more than 500\%.}
    \item {\sl Maintained the \href{https://apps.apple.com/br/app/omni/id1276332750}{Omni + iOS app}. I was able to decrease failures in 86\%, while increasing usage by 7\% (metrics from App Store Connect).}
    \item {\sl Maintained various iOS apps developed with Swift and Objective-C.}
  \end{itemize}

  {\bf DB1 Global Software} \hfill {\bf Apr 2017---Jun 2018} \\
  Software Developer @ CNA \hfill {\sl Maring\'a, PR}\\[-6pt]
  \begin{itemize}
    \item {\sl Designed and built a scalable chat platform used by web clients of \href{https://www.cnago.com.br}{CNA GO}, an online language-learning platform.}
    \item {\sl Developed an integration with a payment hub for
               bank slip and credit card payments.}
  \end{itemize}

  {\bf DB1 Global Software} \hfill {\bf Jul 2013---Mar 2017} \\
  Software Developer @ Consignet \hfill {\sl Maring\'a, PR}\\[-6pt]
  \begin{itemize}
    \item {\sl Developed new features which involved
               frontend and backend development.}
    \item {\sl Designed and built new tools to improve the team productivity.}
    \item {\sl Mentored new team members.}
  \end{itemize}

  {\bf Strada Solu\c{c}\~oes em Tecnologia} \hfill {\bf Jan 2011---Jun 2013} \\
  Test Analyst \hfill {\sl Maring\'a, PR}\\[-6pt]
    \begin{itemize}
    \item {\sl Wrote, executed and automated test cases.}
  \end{itemize}


\section{EDUCATION}
  {\bf Udacity} \hfill {\sl Online} \\
  {\sl ARKit Nanodegree} \hfill {\sl Nov 2017---Dec 2017}\\[6pt]
  {\bf Udacity} \hfill {\sl Online} \\
  {\sl Machine Learning Nanodegree} \hfill {\sl Nov 2016---Sep 2017}\\[6pt]
  {\bf Unicesumar} \hfill {\sl Maring\'a, PR} \\
  {\sl System Analysis and Development} \hfill {\sl 2016}\\[6pt]
  {\bf State University of Maringa} \hfill {\sl Maring\'a, PR} \\
  {\sl Computer Science} \hfill {\sl Feb 2011---Jun 2015}


\section{INDEPENDENT \\ PROJECTS}
  {\bf \href{https://apps.apple.com/us/app/musicsmart/id1512195368}{MusicSmart}} \hfill {\bf Mar 2020---Present} \\
  iOS/iPadOS Application \hfill {\sl Maring\'a, PR}\\[-6pt]
    \begin{itemize}
    \item {\sl An iOS music utility that aggregates and shows credits and additional details about albums and songs from your Apple Music or Spotify music library.}
    \item {\sl Featured on \href{https://www.macstories.net/reviews/musicsmart-puts-the-spotlight-on-music-credits/}{MacStories}, \href{https://9to5mac.com/2020/05/19/musicsmart-apple-music-app/}{9to5Mac}, \href{https://macmagazine.uol.com.br/post/2020/05/21/aplicativo-brasileiro-musicsmart-traz-detalhes-aprofundados-sobre-as-cancoes-do-apple-music/}{MacMagazine} and \href{https://twitter.com/chockenberry/status/1262803700658999296}{more}.}
    \item {\sl Reached 3rd place among the most downloaded paid apps in the Music category in the United States (May 20, 2020).}
    \end{itemize}
  
  {\bf \href{https://apps.apple.com/us/app/musicharbor/id1440405750}{MusicHarbor}} \hfill {\bf Jun 2018---Present} \\
  iOS/iPadOS/macOS Application \hfill {\sl Maring\'a, PR}\\[-6pt]
    \begin{itemize}
    \item {\sl App Store featured app that integrates with Apple Music and Spotify to track new music releases,  music videos,  events and news from your favorite artists.}
    \item {\sl Selected as App of The Year 2020 by the MacStories Team.}
    \item {\sl Featured on the App Store section "\href{https://github.com/marcosatanaka/resume-latex/blob/master/images/apps_we_love_right_now.png?raw=true}{Apps We Love Right Now}".}
    \item {\sl Featured on the App Store article "\href{https://apps.apple.com/us/story/id1516537723}{Apps for the Weekend}".}
    \item {\sl More than 2,100 reviews globally, with an average of 4.7 stars.}
    \end{itemize}

  {\bf \href{https://itunes.apple.com/us/app/really-simple-finance/id1370859710}{Really Simple Finance}} \hfill {\bf Mar 2018---Apr 2018} \\
  iOS Application \hfill {\sl Maring\'a, PR}\\[6pt]
  Really Simple Finance is an iOS app designed to be a simple and easy to use finance tracker.
  It has cool animations and visual effects to enhance the user experience.

  {\bf \href{https://itunes.apple.com/us/app/kiwi-queue/id1352747116}{Kiwi Queue}} \hfill {\bf Feb 2018---Mar 2018} \\
  iOS Application \hfill {\sl Maring\'a, PR}\\[6pt]
  Kiwi Queue is an iOS app to organize and watch YouTube subscriptions.
  It has a triage feature where users can decide between discard or watch later.  This app is no longer available.


\section{SKILLS}
  {\sl {\bf Languages:}} Swift, Java, JavaScript, SQL, HTML, CSS \\
  {\sl {\bf Data Technology:}} Core Data, CloudKit, Redis, Oracle, PostgreSQL \\
  {\sl {\bf Frameworks:}} UIKit, SwiftUI, WidgetKit, Intents (SiriKit), In-App Purchase, CoreSpotlight, Local Notifications, MediaPlayer, MapKit, BackgroundTasks, Alamofire, ObjectMapper, Realm, RxSwift \\
  {\sl {\bf Tools:}} Xcode, Instruments, CocoaPods, Git, IntelliJ


\section{SELECTED \\ AWARDS}             
  {\sl \href{https://www.macstories.net/stories/macstories-selects-2020-recognizing-the-best-apps-of-the-year/#app-of-the-year}{MacStories Selects 2020: App of the Year}}\\
  {\sl \href{https://www.macstories.net/stories/macstories-selects-2019-recognizing-the-best-apps-of-the-year/#app-of-the-year-runner-up}{MacStories Selects 2019: App of the Year (runner-up)}}\\
  {\sl \href{https://mestredoscodigos.com.br/primeira-entrega-dos-pins-do-mestre-dos-codigos}{Mestre dos C\'odigos - Java}:} Awarded by DB1 Global Software.\\
  {\sl \href{https://mestredoscodigos.com.br/primeira-entrega-dos-pins-do-mestre-dos-codigos}{Mestre dos C\'odigos - JavaScript}:} Awarded by DB1 Global Software.\\
 

\end{resume}
\end{document}







